%wikipedia
%\bibitem{wikiSpin} \href{http://en.wikipedia.org/wiki/Spin\_(physics)}{http://en.wikipedia.org/wiki/Spin\_(physics)}
\bibitem{wikiSpin} Griffiths, David (2005). Introduction to Quantum Mechanics (2nd ed.). pp. 1834.			
%\bibitem{wikiAngMom} \href{http://en.wikipedia.org/wiki/Angular\_momentum}{http://en.wikipedia.org/wiki/Angular\_momentum}	
\bibitem{wikiAngMom} Smith, Donald Ray; Truesdell, Clifford (1993). An introduction to continuum mechanics - after Truesdell and Noll. Springer. ISBN 0-7923-2454-4.		
%\bibitem{wikiCoupling} \href{https://en.wikipedia.org/wiki/Coupling\_constant}{https://en.wikipedia.org/wiki/Coupling\_constant}
\bibitem{wikiCoupling} D.J. Gross, F. Wilczek (1973). "Ultraviolet behavior of non-abelian gauge theories". Physical Review Letters 30 (26): 13431346. 
\bibitem{wikiDeut} \href{http://en.wikipedia.org/wiki/Deuterium}{http://en.wikipedia.org/wiki/Deuterium}	
%\bibitem{wikiDNP_wb} \href{http://en.wikipedia.org/wiki/Dynamic\_nuclear\_polarisation}{http://en.wikipedia.org/wiki/Dynamic\_nuclear\_polarisation}
\bibitem{wikiDNP_wb} Goldman, Maurice (1970). Spin Temperature and Nuclear Magnetic Resonance in Solids. Oxford University Press. ISBN 0-19-851251-1.
\bibitem{wikiLQCD} \href{http://en.wikipedia.org/wiki/Lattice\_gauge\_theory}{http://en.wikipedia.org/wiki/Lattice\_gauge\_theory}	
%\bibitem{wikiAsymFree} \href{http://en.wikipedia.org/wiki/Asymptotic\_freedom}{http://en.wikipedia.org/wiki/Asymptotic\_freedom}		
\bibitem{wikiAsymFree} D.J. Gross, F. Wilczek (1973). "Ultraviolet behavior of non-abelian gauge theories". Physical Review Letters 30 (26): 13431346. 


%hyperphysics
\bibitem{hyperDeut} \href{http://hyperphysics.phy-astr.gsu.edu/hbase/particles/deuteron.html}{http://hyperphysics.phy-astr.gsu.edu/hbase/particles/deuteron.html}


%Theses
\bibitem{bDey_th} B. ~Dey, Differential cross section and polarization extractions for $\gamma p \rightarrow K^{+} \Sigma^{0}$ and $\gamma p \rightarrow \phi p$ using CLAS at Jefferson Lab, towards a partial wave analysis in search of missing baryon resonances, PhD thesis, Carnegie Mellon University, (2011) %Biplab Dey
\bibitem{nGuler_th} N. ~Guler, Spin Structure of the Deuteron, PhD thesis, Old Dominion University, (2009)
\bibitem{jxZhang_th} J. ~Zhang, Exclusive $\pi^-$ Electro-production from the Neutron in the Resonance Region.
        PhD thesis, Old Dominion University, (2010)
\bibitem{kSliferTh} K. ~Slifer, A Measurement of the Extended GDH Integral and the Burkhardt-Cottingham Sum Rule.
        PhD thesis, Temple University, (2004)        
\bibitem{mWilliams_th} \href{http://wwwold.jlab.org/Hall-B/general/clas\_thesis.html}{M. ~Williams}, 
	Measurement of Differential Cross Sections and Spin Density Matrix Elements along with a Partial Wave Analysis for $\gamma p \rightarrow p\omega$ using CLAS at Jefferson Lab. 
        PhD thesis, Carnegie Mellon University, (2007)
\bibitem{rdVita_th} X. ~Zheng, Measurement of the Double Spin Asymmetry in $\pi^+$ electroproduction with CLAS, 
        PhD thesis, University of Genova, (2000)
\bibitem{rfersch_th} R. ~G. ~Fersch, ~Jr. Measurement of Inclusive Proton Double-Spin Asymmetries and Polarized Structure Functions.
        PhD thesis, College of William and Mary, (2008)
\bibitem{vipuliTh} K.G. Vipuli G. Dharmawardane. Spin Structure Functions of the Deuteron Measured with CLAS in and above the Resonance region. PhD thesis, Old Dominion University, (2004)
\bibitem{vSulkoskyTh} V. A. ~Sulkosky, The Spin Structure of $^3He$ and the neutron at low \qsq: A measurment of the generalized GDH integrand.
        PhD thesis, Temple University, (2007)  
\bibitem{xzheng_th} X. ~Zheng, Precision Measurement of Neutron Spin Asymmetry $A_1^n$ at Large $x_{Bj}$ Using CEBAF at 5.7 GeV.
        PhD thesis, Massachusetts Institute of Techology, (2002)
\bibitem{yProk_th} Y. A. ~Prok, Measurement of the Spin Structure Function $g_1(x,Q^2)$ of the Proton in the Resonance Region,
        PhD thesis, University of Virgina, (2004)



%Books
\bibitem{bkPovh} B. Povh, K. rith, C. Scholz, F. Zetsche, Particles and Nuclei, Springer, 2002. 3.%Springer-Verlag Berlin Heidelberg, 2002. 3.


%Classic papers
\bibitem{GDHsumRule} S. Gerasimov. Yad. Fiz. 2 598 (1965). S. D. Drell and A. C. Hearn. Phys. Rev. Lett. 16 908 (1966).
\bibitem{opeWilson} K. Wilson (1964), unpublished Cornell Report and Phys. Rev. 179 (1969) 1499. 


% CLAS-notes:
\bibitem{cnKEgiyan} K.S. Egiyan, \href{http://www.jlab.org/Hall-B/notes/clas_notes99/ec_thresh.ps}{CLAS-NOTE-1999-007 - 1999.}
\bibitem{cnDoughty} D. C. Doughty Jr., \etal, A VXIbus Based Trigger for the CLAS Detector at CEBAF, 
           \href{http://wwwold.jlab.org/Hall-B/notes/clas\_notes91/note91-017.pdf}{CLAS-NOTE-91-017, 1991.}
\bibitem{bostedBckgCont} P. Bosted, Pair-Symmetric and Pion Backgrounds for EG1b, \href{http://www.jlab.org/Hall-B/notes/clas\_notes04/2004-005.ps}{CLAS-NOTE-2004-005, 2004.}
\bibitem{cnOsipenko} M. Osipenko, A. Vlassov and and M. Taiuti\href{http://www.jlab.org/Hall-B/notes/clas_notes04/2004-020.pdf}{CLAS NOTE 2004-020 - 2004.}




%Papers:
\bibitem{MBurkardtG2} M. Burkardt (2009). "The \gtwo Structure Function", \href{http://arxiv.org/abs/0905.4079}{arXiv:0905.4079v1 [hep-ph]}
\bibitem{DrechselSmRlPol} D. Drechsel (2009). "Spin Sum Rules and Polarizabilites", \href{http://arxiv.org/abs/0910.0719}{arXiv:0910.0719v1 [nucl-th]}
\bibitem{DrechselPasqVan} D. Drechsel, B. Pasquini, M. Vanderhaeghen. "Dispersion relations in real and virtual Compton scattering", \href{http://arxiv.org/abs/hep-ph/0212124}{arXiv:hep-ph/0212124v1}
\bibitem{pArenhovel1} H. Arenhövel. Phys. Lett. \textbf{B595} (2004) 
%\bibitem{pArenhovelEtAl1} H. Arenhövel {\em et al.} Phys. Rev. Lett. 93, 202301 (2004).
\bibitem{pArenhovelEtAl1} H. Arenhövel \etal. Phys. Rev. Lett. 93, 202301 (2004).
\bibitem{pLeaderKuhnChen} S.E. Kuhn, J.P. Chen, E. Leader (2009). ``Spin Structure of the Nucleon -Status and Recent Results''. arXiv;0812.3535v2
\bibitem{pKarliner} Phys. Rev. D7, 2717 (1973)
\bibitem{pWorkmanArndt} Phys. Rev. D45, 1789 (1992)
\bibitem{pCiofiEtal1} C. Ciofi degli Atti \etal. Phys. Lett. B404, 223 (1997)
\bibitem{clasEC_nim} M. Amarian et al., The CLAS forward electromagnetic calorimeter, 
                \href{http://www.sciencedirect.com/science/article/pii/S0168900200009967}{Nucl. Instr. And Meth. 460 (2000) 239-265.}
\bibitem{clasBrooks} W. Brooks, The CEBAF Large Acceptance Spectrometer for Intermediate Energy Electromagnetic Nuclear Physics.
\bibitem{clasMecking} B. A. Mecking, CLAS - A Large Acceptance Spectrometer (CLAS),
                 \href{http://www.sciencedirect.com/science/article/pii/S0168900203010015}{Nucl. Instr. And Meth. 503/3 (2003)}
\bibitem{targetNIM} C. D. Keith et al., A polarized target for the CLAS detector, 
                 \href{https://userweb.jlab.org/\~ckeith/EG1/nim.pdf}{Nucl. Instr. And Meth. 501 (2003) 327-339}
\bibitem{CEBAFanRev} C. Leeman, D. Douglas, G. Krafft, The Continuous Electron Beam Accelerator Facility:
            CEBAF at the Jefferson Laboratory, Ann. Rev. Nucl. Part. Sci. 2001. 51:413-50
\bibitem{KahnEtal} Y. Kahn, W. Melnitchouk and S. A. Kulagin, “New method for extracting neutron structure functions from nuclear data,” Phys. Rev. C 79, 035205 (2009) \href{http://arxiv.org/abs/0809.4308}{[arXiv:nucl-th/0809.4308]}.

% Models (Theory)
\bibitem{AnselIoffeLeader} M. Anselmino, B. L. Ioffe, and E. Leader, Sov. J. Nucl. Phys. {\bf 49}, 136 (1989)
\bibitem{BEKM13} V. Bernard, E. Epelbaum, H. Krebs, U. Meissner, \href{http://arxiv.org/abs/1209.2523}{Phys. Rev. D \textbf{87}, 054032 (2013) }
\bibitem{BHM03} V. Bernard, T. R. Hemmert, and U.-G. Meissner, Phys. Rev. D67, 076008 (2003)
\bibitem{Burk01} V. D. Burkert, \href{http://arxiv.org/abs/nucl-th/0004001}{Phys. Rev. D63, 097904 (2001)}.
\bibitem{BurkIoffe92} V. D. Burkert and B. L. Ioffe, \href{http://www.jlab.org/div\_dept/admin/publications/papers/92/PR92-018.pdf}{Phys. Lett. \textbf{B296}, 223 (1992)}
\bibitem{BurkIoffe94} V. D. Burkert and B. L. Ioffe, J. Exp. Theor. Phys. \textbf{78}, 619 (1994)
\bibitem{KaoPV04} C. W. Kao, B. Pasquini, M. Vanderhaeghen, \href{http://arxiv.org/abs/hep-ph/0408095}{Phys. Rev. D \textbf{70}, 114004 (2004)}
\bibitem{KaoSpzVan03} C. W. Kao, T. Spitzenberg, M. Vanderhaeghen, \href{http://prd.aps.org/abstract/PRD/v67/i1/e016001}{Phys. Rev. D \textbf{67}, 016001 (2004)}
\bibitem{maid07} D. Drechsel, S.S. Kamalov, and L. Tiator, Eur. Phys. J. A \textbf{34}, 6997 (2007)
\bibitem{maidTech} L. Tiator and Sabit Kamalov, “MAID ANALYSIS TECHNIQUESn", arXiv:nucl-th/0603012v1
\bibitem{soffTerr02} J. Soffer and O. V. Teryaev, \href{http://arxiv.org/pdf/hep-ph/0207252.pdf}{Phys. Lett. {\bf B545}, 323 (2002)}
\bibitem{STP10} R. S. Pasechnik, J. Soffer and O. V. Teryaev, \href{http://arxiv.org/abs/1009.3355}{Phys. Rev. D \textbf{82}, 076007 (2010)}


% PDG reviews
\bibitem{pdg12} J. Beringer et al. (Particle Data Group), \href{http://pdg.lbl.gov/2012/reviews/rpp2012-rev-n-delta-resonances.pdf}{Phys. Rev. D86, 010001 (2012)}  %(Should I use the following instead? that particular document is only a part of this bigger/complete 2012 review APS article http://prd.aps.org/pdf/PRD/v86/i1/e010001)
\bibitem{pdg11strFn} K. Nakamura et al. (PDG), \href{http://pdg.lbl.gov/2011/reviews/rpp2011-rev-structure-functions.pdf}{JP G37, 075021 (2010) and 2011 partial update for the 2012 edition}
\bibitem{pdg12Res} J. Beringer et al. (PDG), \href{http://pdg.lbl.gov/2012/reviews/rpp2012-rev-n-delta-resonances.pdf}{PR \textbf{D86}, 010001 (2012)}



%From Proceedings 
\bibitem{procKazimi}\href{http://accelconf.web.cern.ch/AccelConf/e04/PAPERS/TUPLT164.PDF}
        {R. Kazimi \etal}. CEBAF Injector Achieved World's Best Beam Quality for Three Simultaneous Beams with 
        a Wide Range of Bunch Charges, Proceedings of EPAC 2004, Lucerne, Switzerland
\bibitem{HosodaYamamoto66} M. Hosoda and K. Yamamoto, Prog. Theor. Phys. (Kyoto) \textbf{30}, 425 (1966)
\bibitem{KuhnHUGS} S. E. Kuhn, Nucleon Structure Functions: Experiments and Models, Proceedings of the 12th Annual HUGS at CEBAF, 1997
\bibitem{bkAnselmino} M. Anselmino \etal Three-Dimensional Partonic Structure of the Nucleon, Proceedings of the International School of Physics "Enrico Fermi", 2011, Varenna On Lake Como Italy.%IOS Press, 2012 %http://books.google.com/books?id=h1Te-D5Nf-EC&printsec=frontcover#v=onepage&q&f=false

% Technotes
\bibitem{KuhnEG4ana} S. E. Kuhn, K. Adhikari,Data Analysis for EG4 - extraction of g1 from data \href{https://userweb.jlab.org/\~kuhn/EG4/EG4\_analysis.pdf}{https://clasweb.jlab.org/rungroups/eg4/wiki/index.php/Technotes\_and\_Reports}


%Proposals:
\bibitem{propE06_017} A. Deur, et al. 2005 Jefferson Lab proposal PR06-017  % The deuteron-target EG4 proposal
\bibitem{propE03_006} M.Battaglieri, et al. 2003 Jefferson Lab proposal E03-006 %The proton-target EG4 proposal
\bibitem{propE97_110} J.P. Chen, et al. 1997 Jefferson Lab proposal PR97-110 
%Available at http://hallaweb.jlab.org/physics/experiments/he3/gdh/PR97-110.pdf


%Websites
\bibitem{eg4Hm_wb} \href{http://clasweb.jlab.org/shift/eg4/}{http://clasweb.jlab.org/shift/eg4/}
\bibitem{eg4wiki} \href{https://clasweb.jlab.org/rungroups/eg4/wiki/index.php/Main\_Page}{https://clasweb.jlab.org/rungroups/eg4/wiki/index.php/Main\_Page}
\bibitem{cebaf2_wb} \href{http://www.aip.org/png/html/cebaf.htm}{http://www.aip.org/png/html/cebaf.htm}
%\bibitem{kuhnDvcs_wb} http://clasweb.jlab.org/rungroups/eg1-dvcs/wiki/index.php/\\Raster$\_$Correction:$\_$last$\_$update$\_$June$\_$16$\_$2009
%\bibitem{gsimMH_wb} M. Holtrop, GSIM: CLAS GEANT Simulation, \href{http://nuclear.unh.edu/\textasciitilde maurik/gsim\_info.shtml}{http://nuclear.unh.edu/\~maurik/gsim\_info.shtml} 
\bibitem{gsimMH_wb} M. Holtrop, GSIM: CLAS GEANT Simulation, \url{http://nuclear.unh.edu/\~maurik/gsim\_info.shtml}
%http://tex.stackexchange.com/questions/9363/how-does-one-insert-a-backslash-or-a-tilde-into-latex
% Solved the tilda problem using 'url' (got idea from above link & http://en.wikibooks.org/wiki/LaTeX/Hyperlinks#.5Curl)
\bibitem{jlabVocab_wb} \href{http://www.jlab.org/news/facts/vocab.html}{http://www.jlab.org/news/facts/vocab.html}
%\bibitem{DC1_wb} \href{http://www-meg.phys.cmu.edu/\textasciitilde bellis/dc/dcintro.html}{http://www-meg.phys.cmu.edu/\~bellis/dc/dcintro.html}  %Tilda didn't work right with href, so I am using the following 
\bibitem{DC1_wb} \url{http://www-meg.phys.cmu.edu/\~bellis/dc/dcintro.html}
\bibitem{DC2_wb} \href{http://ikpe1101.ikp.kfa-juelich.de/cosy-11/exp/drift\_chambers/DriftChambers\_E.html}
                 {http://ikpe1101.ikp.kfa-juelich.de/cosy-11/exp/drift\_chambers/DriftChambers\_E.html}
\bibitem{uvaTgtHA_wb} \href{https://hallaweb.jlab.org/wiki/index.php/Practical\_Primer\_on\_the\_UVa\_Target}
                 {https://hallaweb.jlab.org/wiki/index.php/Practical\_Primer\_on\_the\_UVa\_Target}
\bibitem{schlpClas_wb} \href{http://www.scholarpedia.org/article/The\_Thomas\_Jefferson\_National\_Accelerator\_Facility}
                     {http://www.scholarpedia.org/article/The\_Thomas\_Jefferson\_National\_Accelerator\_Facility}
\bibitem{bpmMSpata_wb} M. F. Spata, TJNAF, \href{http://cdsweb.cern.ch/record/586314/files/p101.pdf}
                    {http://cdsweb.cern.ch/record/586314/files/p101.pdf}
\bibitem{bpmRUrsicEtc_wb} R. Ursic \etal. \href{http://epaper.kek.jp/pac97/papers/pdf/9P089.PDF}{1 nA Beam Position Monitory System}, TJNAF




% Computation related
\bibitem{bos} V. Blobel \etal. The BOS system for the CLAS detector: Dynamic Memory Management, (1995).



%Private Communications
\bibitem{kuhn_dodge_pc} S. E. Kuhn and G. E. Dodge, Private communications. %Multiply defined error (also defined in bibli.tex in chap6expSetup
\bibitem{pComKuhn} S. E. Kuhn, Private communications.
\bibitem{pComDodge} G. E. Dodge, Private communications.
\bibitem{pComBosted} P. Bosted, Private communications.
\bibitem{deurSlifRip_pc} A. Deur, K. Slifer and M. Ripani (EG4 spokespersons), Private communications.
\bibitem{HK_dXs_extr} \href{http://wwwold.jlab.org/Hall-B/secure/eg4/hkkang/dXs\_extraction\_2nd.pdf}{H. Kang}, Procedure for extraction of difference of cross sections.



%   From: https://userweb.jlab.org/~kuhn/EG4/EG4_analysis.pdf by SEK & KPA
\bibitem{EG4:ref}
M. Anghinolfi \etal ``The GDH Sum Rule with Nearly-Real Photons and the Proton $g_1$ Structure Function at Low Momentum Transfer,'' CLAS Proposal PR-03-006 (2003). %It seems repeated

\bibitem{panal} R. Fersch, 
``Measurement of Inclusive Proton Double-Spin Asymmetries and Polarized Structure Functions in the CLAS EG1b Experiment'', 2012.
URL: {\texttt http://www.jlab.org/Hall-B/secure/eg1/EG2000/fersch/softwarenote/AnalysisNote/}

\bibitem{PolNit:ref} K. Abe \etal, 
Phys. Rev. D \textbf{58}, 112003 (1998).

\bibitem{Mayer}
M. Mayer, CLAS NOTE 2012 - 004 (2012).

\bibitem{Kuchto:ref}
T.V. Kuchto and N.M. Shumeiko, 
``Radiative Effects in Deep Inelastic Scattering of Polarized Leptons by Polarized Nucleons,''
\npb{219}, 412 (1983).

\bibitem{MoTsai:ref} L.W. Mo and Y.S. Tsai, 
``Radiative Corrections to Elastic and Inelastic $ep$ and $\mu p$ Scattering,''
Rev. Mod. Phys. \textbf{41}, 205 (1969).








%============ Following brought from TechNotes/deutContam.tex 
%\bibitem{PDG} Particle Data Group, LBL.
\bibitem{sarahTgt} \href{http://clasweb.jlab.org/rungroups/eg4/wiki/index.php/October\_14\%2C\_2011\#Target\_Composition}{http://clasweb.jlab.org/rungroups/eg4/wiki/index.php/October\_14\%2C\_2011}
\bibitem{bostedD2Cont} \href{http://wwwold.jlab.org/Hall-B/secure/eg1-dvcs/technotes/hind/hind.pdf}{P. Bosted, \nh3 correction for \nd3 target}, EG1-DVCS Technical Note \# 017
\bibitem{koiralaD2Cont} \href{http://wwwold.jlab.org/Hall-B/secure/eg1-dvcs/skoirala/ND3Contam/WideContamDist.gif}{S. Koirala's work on Deuteron contamination (EG1-DVCS)}.
%\bibitem{pComKuhn} S. E. Kuhn, Private communications.
