%kp: 11/27/16 (bibtex or .bib file didn't seem to work with pdflatex in ifarm, so I created this file
%        to have bibitem alternatives to all the entries in bibli2.bib


\bibitem{wikiAngMom} 
         D.R. Smith, ``An introduction to continuum mechanics - after Truesdell and Noll,''
         Springer. ISBN 0-7923-2454-4, (1993)


%wikipedia
%\bibitem{wikiSpin} \href{http://en.wikipedia.org/wiki/Spin\_(physics)}{http://en.wikipedia.org/wiki/Spin\_(physics)}
%\bibitem{wikiSpin} Griffiths, David (2005). Introduction to Quantum Mechanics (2nd ed.). pp. 183–4.	
%It seems both book and inbook entries work the same way (at least in the current style that I am using)
\bibitem{wikiSpin} 
         D.J. Griffiths, Introduction to Quantum Mechanics (2nd ed.). pp. 183–4 
         Pearson Prentice Hall, (2005).


%http://www.sciencedirect.com/science/article/pii/0370269383904379  EMC effect (Chap1 )
%author = "J.J. Aubert and G. Bassompierre and K.H. Becks and C. Best and E. Böhm and X. de Bouard and F.W. Brasse and C. Broll and S. Brown and J. Carr and R.W. Clifft and J.H. Cobb and G. Coignet and F. Combley and G.R. Court and G. D'Agostini and W.D. Dau and J.K. Davies and Y. Déclais and R.W. Dobinson and U. Dosselli and J. Drees and A.W. Edwards and M. Edwards and J. Favier and M.I. Ferrero and W. Flauger and E. Gabathuler and R. Gamet and J. Gayler and V. Gerhardt and C. Gössling and J. Haas and K. Hamacher and P. Hayman and M. Henckes and V. Korbel and U. Landgraf and M. Leenen and M. Maire and H. Minssieux and W. Mohr and H.E. Montgomery and K. Moser and R.P. Mount and P.R. Norton and J. McNicholas and A.M. Osborne and P. Payre and C. Peroni and H. Pessard and U. Pietrzyk and K. Rith and M. Schneegans and T. Sloan and H.E. Stier and W. Stockhausen and J.M. Thénard and J.C. Thompson and L. Urban and M. Villers and H. Wahlen and M. Whalley and D. Williams and W.S.C. Williams and J. Williamson and S.J. Wimpenny"
%url = "http://www.sciencedirect.com/science/article/pii/0370269383904379",
\bibitem{Aubert1983275} 
         J.J. Aubert \etal, The ratio of the nucleon structure functions \{F2N\} for iron and deuterium,
         Science Direct, (1983)        

\bibitem{Ashman1988364}
        J. Ashman \etal, A measurement of the spin asymmetry and determination of the structure function g1 in deep inelastic muon-proton scattering,
        Science Direct, (1988)   


%http://inspirehep.net/record/277487?ln=en EMC collaboration
\bibitem{Piguet:1989va}
        O. Pguet etal, The Cancellation of Nonlocal Divergences in Light Cone Theories,
        Nucl.Phys., B328, pp. 527, (1989)

	
%\bibitem{wikiCoupling} \href{https://en.wikipedia.org/wiki/Coupling\_constant}{https://en.wikipedia.org/wiki/Coupling\_constant}
\bibitem{wikiCoupling} D.J. Gross, F. Wilczek (1973). "Ultraviolet behavior of non-abelian gauge theories". Physical Review Letters 30 (26): 1343–1346. 


\bibitem{wikiDeut2} \href{http://en.wikipedia.org/wiki/Deuterium}{http://en.wikipedia.org/wiki/Deuterium}
	
%http://inspirehep.net/search?p=find+eprint+NUCL-TH/0102049
%article{Garcon:2001sz,
\bibitem{wikiDeut} 
         M. Garcon and J. W. Van Orden, The Deuteron: Structure and form-factors,
         Adv.Nucl.Phys., 26, pp. 293, (2001)


%\bibitem{wikiDNP_wb} \href{http://en.wikipedia.org/wiki/Dynamic\_nuclear\_polarisation}{http://en.wikipedia.org/wiki/Dynamic\_nuclear\_polarisation}
\bibitem{wikiDNP_wb} Goldman, Maurice, Spin Temperature and Nuclear Magnetic Resonance in Solids. Oxford University Press. ISBN 0-19-851251-1, (1970).

\bibitem{wikiLQCD} \href{http://en.wikipedia.org/wiki/Lattice\_gauge\_theory}{http://en.wikipedia.org/wiki/Lattice\_gauge\_theory}	

%http://adsabs.harvard.edu/abs/1974PhRvD..10.2445W (I was led to this from the wiki/LQCD 
%http://prd.aps.org/abstract/PRD/v10/i8/p2445_1  % url = {http://link.aps.org/doi/10.1103/PhysRevD.10.2445},

\bibitem{PhysRevD.10.2445}
     K. G. Wilson, Confinement of quarks, 
     Phys. Rev. D, 10 (8), 2445--2459, (1974)

% http://rmp.aps.org/export/RMP/v82/i2/p1349_1?type=bibtex  http://rmp.aps.org/abstract/RMP/v82/i2/p1349_1  author = {Bazavov, A. and Toussaint, D. and Bernard, C. and Laiho, J. and DeTar, C. and Levkova, L. and Oktay, M. B. and Gottlieb, Steven and Heller, U. M. and Hetrick, J. E. and Mackenzie, P. B. and Sugar, R. and Van de Water, R. S.},

\bibitem{RevModPhys.82.1349}
       A. Bazavov \etal, Nonperturbative QCD simulations with $2+1$ flavors of improved staggered quarks,
       Rev. Mod. Phys., 82 (2), 1349--1417, (2010)

% http://inspirehep.net/search?p=find+eprint+0906.3599 (this too for replacing wikiLQCD)
\bibitem{Durr:2008zz}
        S. Durr \etal, Ab-Initio Determination of Light Hadron Masses, 
        Science, 322,   1224-1227, (2008)    


%http://inspirehep.net/search?p=find+eprint+HEP-PH/0610200 (Again for wikiLQCD)
\bibitem{Meissner:2006sp}
      U. G. Meissner,       Some recent developments in chiral perturbation theory,
      hep-ph/0610200, (2006)

%http://inspirehep.net/search?p=find+eprint+HEP-PH/0611231
\bibitem{Bernard:2006gx}
        V. Bernard, U. G. Meissner, Chiral perturbation theory, 
        Ann.Rev.Nucl.Part.Sci., (2007)

%\bibitem{wikiAsymFree} \href{http://en.wikipedia.org/wiki/Asymptotic\_freedom}{http://en.wikipedia.org/wiki/Asymptotic\_freedom}	
%\bibitem{wikiAsymFree} D.J. Gross, F. Wilczek (1973). "Ultraviolet behavior of non-abelian gauge theories". Physical Review Letters 30 (26): 1343–1346. (see above, with a different label)

%hyperphysics
\bibitem{hyperDeut} \href{http://hyperphysics.phy-astr.gsu.edu/hbase/particles/deuteron.html}{http://hyperphysics.phy-astr.gsu.edu/hbase/particles/deuteron.html}

%Theses
\bibitem{bDey_th} B. ~Dey, Differential cross section and polarization extractions for $\gamma p \rightarrow K^{+} \Sigma^{0}$ and $\gamma p \rightarrow \phi p$ using CLAS at Jefferson Lab, towards a partial wave analysis in search of missing baryon resonances, PhD thesis, Carnegie Mellon University, (2011) %Biplab Dey

\bibitem{nGuler_th} N. ~Guler, Spin Structure of the Deuteron, PhD thesis, Old Dominion University, (2009)

\bibitem{jxZhang_th} J. ~Zhang, Exclusive $\pi^-$ Electro-production from the Neutron in the Resonance Region. PhD thesis, Old Dominion University, (2010)

\bibitem{kSliferTh} K. ~Slifer, A Measurement of the Extended GDH Integral and the Burkhardt-Cottingham Sum Rule. PhD thesis, Temple University, (2004)  


%http://link.springer.com/article/10.1007%2FBF01326984 This and the following are the original paper on Stern Gerlac Exp (The following bibtex entry was obtained by clicking  "Export citations -> Select BibTex (BIB) from the Select Download menu", this will replace the Slifer thesis citation because Dr. Kuhn says it is not the original paper for the subject matter.
% url={http://dx.doi.org/10.1007/BF01326984},     \href{}{
%author={ \href{http://dx.doi.org/10.1007/BF01326984}{Gerlach, Walther and Stern, Otto}},
\bibitem{sternGerlac1922}
        W. Gerlach and O. Stern,         Das magnetische Moment des Silberatoms,
        Zeitschrift für Physik, (1922)

%http://books.google.com/books?id=-_2Wg8lHIucC Used that google book page and clicked on "About this book" and then at the bottom there is Bibliographic information including different links for "Export citation"       url={http://books.google.com/books?id=-\_2Wg8lHIucC}, 
% author={\href{http://books.google.com/books?id=-\_2Wg8lHIucC}{D. Drechsel and L. Tiator}},
\bibitem{drechsel2001gdh}
        Drechsel, D. and Tiator, L.,
        GDH 2000: Proceedings of the Symposium on the Gerasimov-Drell-Hearn Sum Rule and the Nucleon Spin Structure in the Resonance Region : Mainz, Germany, 14-17 June 2000,  
        World Scientific, (2001)
     
\bibitem{mWilliams_th} \href{http://wwwold.jlab.org/Hall-B/general/clas\_thesis.html}{M. ~Williams}, Measurement of Differential Cross Sections and Spin Density Matrix Elements along with a Partial Wave Analysis for $\gamma p \rightarrow p\omega$ using CLAS at Jefferson Lab. PhD thesis, Carnegie Mellon University, (2007)

\bibitem{rdVita_th} R. De Vita, Measurement of the Double Spin Asymmetry in $\pi^+$ electroproduction with CLAS, PhD thesis, University of Genova, (2000)

\bibitem{rfersch_th} R. ~G. ~Fersch, ~Jr. Measurement of Inclusive Proton Double-Spin Asymmetries and Polarized Structure Functions. PhD thesis, The College of William and Mary, (2008)

\bibitem{vipuliTh} K.G. Vipuli G. Dharmawardane. Spin Structure Functions of the Deuteron Measured with CLAS in and above the Resonance region. PhD thesis, Old Dominion University, (2004)

\bibitem{vSulkoskyTh} V. A. ~Sulkosky, The Spin Structure of $^3He$ and the neutron at low \qsq: A measurment of the generalized GDH integrand. PhD thesis, The College of William and Mary, (2007)  

\bibitem{xzheng_th} X. ~Zheng, Precision Measurement of Neutron Spin Asymmetry $A_1^n$ at Large $x_{Bj}$ Using CEBAF at 5.7 GeV.        PhD thesis, Massachusetts Institute of Techology, (2002)

\bibitem{yProk_th} Y. A. ~Prok, Measurement of the Spin Structure Function $g_1(x,Q^2)$ of the Proton in the Resonance Region,         PhD thesis, University of Virgina, (2004)



%Books
\bibitem{bkPovh} B. Povh, K. rith, C. Scholz, F. Zetsche, Particles and Nuclei, Springer, 2002. 3.%Springer-Verlag Berlin Heidelberg, 2002. 3.


%Classic papers
\bibitem{GDHsumRule0} S. Gerasimov. Yad. Fiz. 2 598 (1965). S. D. Drell and A. C. Hearn. Phys. Rev. Lett. 16 908 (1966).

%   url = {http://link.aps.org/doi/10.1103/PhysRevLett.16.908},   \href{}{
\bibitem{GDHsumRule},
        S. D. Drell and A. C. Hearn, Exact Sum Rule for Nucleon Magnetic Moments,
        Phys. Rev. Lett., American Physical Society, (1966)

\bibitem{opeWilson} K. Wilson (1964), unpublished Cornell Report and Phys. Rev. 179 (1969) 1499. 
%article{PhysRev.179.1499,   url = {http://link.aps.org/doi/10.1103/PhysRev.179.1499},




% CLAS-notes:
\bibitem{cnKEgiyan} K.S. Egiyan, \href{http://www.jlab.org/Hall-B/notes/clas_notes99/ec_thresh.ps}{CLAS-NOTE-1999-007 - 1999.}


\bibitem{cnDoughty} D. C. Doughty Jr., \etal, A VXIbus Based Trigger for the CLAS Detector at CEBAF,            \href{http://wwwold.jlab.org/Hall-B/notes/clas\_notes91/note91-017.pdf}{CLAS-NOTE-91-017, 1991.}

\bibitem{bostedBckgCont} P. Bosted, Pair-Symmetric and Pion Backgrounds for EG1b, \href{http://www.jlab.org/Hall-B/notes/clas\_notes04/2004-005.ps}{CLAS-NOTE-2004-005, 2004.}

\bibitem{cnOsipenko} M. Osipenko, A. Vlassov and M. Taiuti\href{http://www.jlab.org/Hall-B/notes/clas_notes04/2004-020.pdf}{CLAS NOTE 2004-020 - 2004.}



%Papers:
\bibitem{MBurkardtG2} M. Burkardt (2009). "The \gtwo Structure Function", \href{http://arxiv.org/abs/0905.4079}{arXiv:0905.4079v1 [hep-ph]}
%article{Burkardt:2009rf,

\bibitem{DrechselSmRlPol} D. Drechsel (2009). "Spin Sum Rules and Polarizabilites", \href{http://arxiv.org/abs/0910.0719}{arXiv:0910.0719v1 [nucl-th]}
%article{Drechsel:2009ch,

\bibitem{DrechselPasqVan} D. Drechsel, B. Pasquini, M. Vanderhaeghen. "Dispersion relations in real and virtual Compton scattering", \href{http://arxiv.org/abs/hep-ph/0212124}{arXiv:hep-ph/0212124v1}

\bibitem{pArenhovel1} H. Arenhövel. Phys. Lett. \textbf{B595} (2004) 
%article{Arenhoevel:2004zn,

\bibitem{pArenhovelEtAl1} H. Arenhövel {\em et al.} Phys. Rev. Lett. 93, 202301 (2004).
%\bibitem{pArenhovelEtAl1} H. Arenhövel \etal. Phys. Rev. Lett. 93, 202301 (2004).
%article{PhysRevLett.93.202301,       \href{}{            url = {http://link.aps.org/doi/10.1103/PhysRevLett.93.202301}, 

\bibitem{pLeaderKuhnChen} S.E. Kuhn, J.P. Chen, E. Leader (2009). ``Spin Structure of the Nucleon -Status and Recent Results''. arXiv;0812.3535v2
%article{Kuhn:2008sy,

\bibitem{pKarliner} 
        Karliner, Inga, Saturation of the Drell-Hearn-Gerasimov Sum Rule
        Phys. Rev. D7, 2717 (1973)
%article{PhysRevD.7.2717,    url = {http://link.aps.org/doi/10.1103/PhysRevD.7.2717},    \href{}{           

\bibitem{pWorkmanArndt} 
         Workman, Ron L. and Arndt, Richard A., Saturation of the Drell-Hearn-Gerasimov sum rule reexamined
         Phys. Rev. D45, American Physical Society, 1789 (1992)
%article{PhysRevD.45.1789,          url = {http://link.aps.org/doi/10.1103/PhysRevD.45.1789},  

\bibitem{pCiofiEtal1} C. Ciofi degli Atti \etal. 
       On the extraction of the neutron spin structure functions and the Gerasimov-Drell-Hearn integral from the process in the resonance region
       Phys. Lett. B404, 223 (1997)
%article{CiofidegliAtti1997223,        url = "http://www.sciencedirect.com/science/article/pii/S0370269397005765",

\bibitem{clasBrooks} W. Brooks, The CEBAF Large Acceptance Spectrometer for Intermediate Energy Electromagnetic Nuclear Physics. %http://www.osti.gov/scitech/biblio/754039#        url={http://www.osti.gov/scitech/servlets/purl/754039}, 
%inbook{Brooks_1999, 
                     (1999)

%article{Amarian2001239, title = "The \{CLAS\} forward electromagnetic calorimeter ",  url = "http://www.sciencedirect.com/science/article/pii/S0168900200009967",
%author = "M. Amarian and G. Asryan and K. Beard and W. Brooks and V. Burkert and T. Carstens and A. Coleman and R. Demirchyan and Yu. Efremenko and H. Egiyan and K. Egiyan and H. Funsten and V. Gavrilov and K. Giovanetti and R.M. Marshall and B. Mecking and R.C. Minehart and H. Mkrtchan and M. Ohandjanyan and Yu. Sharabian and L.C. Smith and S. Stepanyan and W.A. Stephens and T.Y. Tung and C. Zorn",
\bibitem{clasEC_nim}
        M. Amarian \etal, The {CLAS} forward electromagnetic calorimeter,
        Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment, (2001)


\bibitem{clasMecking} B. A. Mecking, CLAS - A Large Acceptance Spectrometer (CLAS),                 \href{http://www.sciencedirect.com/science/article/pii/S0168900203010015}{Nucl. Instr. And Meth. 503/3 (2003)}
%article{Mecking2003513,  author = "B.A. Mecking and G. Adams and S. Ahmad and E. Anciant and M. Anghinolfi and B. Asavapibhop and G. Asryan and G. Audit and T. Auger and H. Avakian and J.P. Ball and F.J. Barbosa and S. Barrow and M. Battaglieri and K. Beard and B.L. Berman and N. Bianchi and S. Boiarinov and P. Bonneau and W.J. Briscoe and W.K. Brooks and V.D. Burkert and D.S. Carman and T. Carstens and C. Cetina and S.B. Christo and P.L. Cole and A. Coleman and J. Connelly and D. Cords and P. Corvisiero and D. Crabb and H. Crannell and R.C. Cuevas and P.V. Degtyarenko and L. Dennis and E. DeSanctis and R. DeVita and J. Distelbrink and G.E. Dodge and W. Dodge and G. Doolittle and D. Doughty and M. Dugger and W.S. Duncan and S. Dytman and H. Egiyan and K.S. Egiyan and L. Elouadrhiri and R.J. Feuerbach and J. Ficenec and V. Frolov and H. Funsten and G.P. Gilfoyle and K.L. Giovanetti and E. Golovatch and J. Gram and M. Guidal and V. Gyurjyan and D. Heddle and P. Hemler and F.W. Hersman and K. Hicks and R.S. Hicks and M. Holtrop and C.E. Hyde-Wright and D. Insley and M.M. Ito and G. Jacobs and D. Jenkins and K. Joo and D. Joyce and D. Kashy and M. Khandaker and W. Kim and A. Klein and F.J. Klein and M. Klusman and M. Kossov and L. Kramer and V. Koubarovski and S.E. Kuhn and A. Lake and D. Lawrence and A. Longhi and K. Lukashin and J. Lachniet and R.A. Magahiz and W. Major and J.J. Manak and C. Marchand and C. Martin and S.K. Matthews and M. McMullen and J.W.C. McNabb and M.D. Mestayer and R. Minehart and M. Mirazita and R. Miskimen and V. Muccifora and J. Mueller and L.Y. Murphy and G.S. Mutchler and J. Napolitano and I. Niculescu and B.B. Niczyporuk and M. Nozar and J.T. O'Brien and A.K. Opper and J.E. O'Meara and E. Pasyuk and S.A. Philips and E. Polli and J.W. Price and S. Pozdniakov and L.M. Qin and B.A. Raue and G. Riccardi and G. Ricco and C. Riggs and M. Ripani and B.G. Ritchie and J. Robb and F. Ronchetti and P. Rossi and F. Roudot and C. Salgado and V. Sapunenko and R.A. Schumacher and V.S. Serov and Y.G. Sharabian and E.S. Smith and L.C. Smith and T. Smith and D.I. Sober and A. Stavinsky and S. Stepanyan and P. Stoler and M. Taiuti and W.M. Taylor and S. Taylor and D.J. Tedeschi and U. Thoma and R. Thompson and D. Tilles and L. Todor and T.Y. Tung and W. Tuzel and M.F. Vineyard and A.V. Vlassov and L.B. Weinstein and R.E. Welsh and D.P. Weygand and G.R. Wilkin and M. Witkowski and E. Wolin and A. Yegneswaran and P. Yergin and J. Yun",             url = "http://www.sciencedirect.com/science/article/pii/S0168900203010015",

\bibitem{targetNIM} C. D. Keith et al., A polarized target for the CLAS detector,                \href{https://userweb.jlab.org/\~ckeith/EG1/nim.pdf}{Nucl. Instr. And Meth. 501 (2003) 327-339}
%article{Keith:2003ca,       author         = "Keith, C.D. and Anghinolfi, M. and Battaglieri, M. and Bosted, Peter E. and Branford, D. and others",


\bibitem{CEBAFanRev} C. Leeman, D. Douglas, G. Krafft, The Continuous Electron Beam Accelerator Facility: CEBAF at the Jefferson Laboratory, Ann. Rev. Nucl. Part. Sci. 2001. 51:413-50     URL = {http://www.annualreviews.org/doi/abs/10.1146/annurev.nucl.51.101701.132327},   eprint = {http://www.annualreviews.org/doi/pdf/10.1146/annurev.nucl.51.101701.132327}
%article{doi:10.1146/annurev.nucl.51.101701.132327,

\bibitem{KahnEtal} Y. Kahn, W. Melnitchouk and S. A. Kulagin, “New method for extracting neutron structure functions from nuclear data,” Phys. Rev. C 79, 035205 (2009) \href{http://arxiv.org/abs/0809.4308}{[arXiv:nucl-th/0809.4308]}.
%article{Kahn:2008nq,

% Models (Theory)
\bibitem{AnselIoffeLeader} M. Anselmino, B. L. Ioffe, and E. Leader, Sov. J. Nucl. Phys. {\bf 49}, 136 (1989) %http://inspirehep.net/record/262724/export/hx
%article{Anselmino:1988hn,

\bibitem{BEKM13} V. Bernard, E. Epelbaum, H. Krebs, U. Meissner, \href{http://arxiv.org/abs/1209.2523}{Phys. Rev. D \textbf{87}, 054032 (2013) }
%article{Bernard:2012hb,

\bibitem{BHM03} V. Bernard, T. R. Hemmert, and U.-G. Meissner, Phys. Rev. D67, 076008 (2003)
%article{Bernard:2002pw,

\bibitem{Burk01} V. D. Burkert, \href{http://arxiv.org/abs/nucl-th/0004001}{Phys. Rev. D63, 097904 (2001)}.
%article{Burkert:2000qm,

\bibitem{BurkIoffe92} V. D. Burkert and B. L. Ioffe, \href{http://www.jlab.org/div\_dept/admin/publications/papers/92/PR92-018.pdf}{Phys. Lett. \textbf{B296}, 223 (1992)}  % OriginalText = \bibitem{BURK} V.D.~Burkert and B.L~Ioffe, Phys. Lett. B296, 223(1992); J. Exp. Theo. Phys. 78, 619(1992). http://www.jlab.org/div_dept/physics_division/pCDR_public/Hall_B/Files_&_Figures/cdr0/physics/formfactors/bibl.bib
%article{Burkert:1992tg,

\bibitem{BurkIoffe94} V. D. Burkert and B. L. Ioffe, J. Exp. Theor. Phys. \textbf{78}, 619 (1994)
%article{Burkert:1993ya,

\bibitem{KaoPV04} C. W. Kao, B. Pasquini, M. Vanderhaeghen, \href{http://arxiv.org/abs/hep-ph/0408095}{Phys. Rev. D \textbf{70}, 114004 (2004)}
%article{Kao:2004us,

\bibitem{KaoSpzVan03} C. W. Kao, T. Spitzenberg, M. Vanderhaeghen, \href{http://prd.aps.org/abstract/PRD/v67/i1/e016001}{Phys. Rev. D \textbf{67}, 016001 (2004)}       url = {http://link.aps.org/doi/10.1103/PhysRevD.67.016001}, author = {\href{http://link.aps.org/doi/10.1103/PhysRevD.67.016001}{Kao, Chung Wen and Spitzenberg, Thomas and Vanderhaeghen, Marc}},
%article{PhysRevD.67.016001,

\bibitem{maid07} D. Drechsel, S.S. Kamalov, and L. Tiator, Eur. Phys. J. A \textbf{34}, 69–97 (2007)
%article{Drechsel:2007if,

\bibitem{maidTech} L. Tiator and Sabit Kamalov, “MAID ANALYSIS TECHNIQUESn", arXiv:nucl-th/0603012v1
%article{Tiator:2006dq,


\bibitem{soffTerr02} J. Soffer and O. V. Teryaev, \href{http://arxiv.org/pdf/hep-ph/0207252.pdf}{Phys. Lett. {\bf B545}, 323 (2002)}
%article{Soffer:2002az,

\bibitem{STP10} R. S. Pasechnik, J. Soffer and O. V. Teryaev, \href{http://arxiv.org/abs/1009.3355}{Phys. Rev. D \textbf{82}, 076007 (2010)}
%article{Pasechnik:2010fg,





% PDG reviews
\bibitem{pdg12} J. Beringer et al. (Particle Data Group), \href{http://pdg.lbl.gov/2012/reviews/rpp2012-rev-n-delta-resonances.pdf}{Phys. Rev. D86, 010001 (2012)}  %(Should I use the following instead? that particular document is only a part of this bigger/complete 2012 review APS article http://prd.aps.org/pdf/PRD/v86/i1/e010001)
%article{PhysRevD.86.010001,         author = {Beringer, J. and Arguin, J. -F. and Barnett, R. M. and Copic, K. and Dahl, O. and Groom, D. E. and Lin, C. -J. and Lys, J. and Murayama, H. and Wohl, C. G. and Yao, W. -M. and Zyla, P. A. and Amsler, C. and Antonelli, M. and Asner, D. M. and Baer, H. and Band, H. R. and Basaglia, T. and Bauer, C. W. and Beatty, J. J. and Belousov, V. I. and Bergren, E. and Bernardi, G. and Bertl, W. and Bethke, S. and Bichsel, H. and Biebel, O. and Blucher, E. and Blusk, S. and Brooijmans, G. and Buchmueller, O. and Cahn, R. N. and Carena, M. and Ceccucci, A. and Chakraborty, D. and Chen, M. -C. and Chivukula, R. S. and Cowan, G. and D'Ambrosio, G. and Damour, T. and de Florian, D. and de Gouv\^ea, A. and DeGrand, T. and de Jong, P. and Dissertori, G. and Dobrescu, B. and Doser, M. and Drees, M. and Edwards, D. A. and Eidelman, S. and Erler, J. and Ezhela, V. V. and Fetscher, W. and Fields, B. D. and Foster, B. and Gaisser, T. K. and Garren, L. and Gerber, H. -J. and Gerbier, G. and Gherghetta, T. and Golwala, S. and Goodman, M. and Grab, C. and Gritsan, A. V. and Grivaz, J. -F. and Gr\"unewald, M. and Gurtu, A. and Gutsche, T. and Haber, H. E. and Hagiwara, K. and Hagmann, C. and Hanhart, C. and Hashimoto, S. and Hayes, K. G. and Heffner, M. and Heltsley, B. and Hern\'andez-Rey, J. J. and Hikasa, K. and H\"ocker, A. and Holder, J. and Holtkamp, A. and Huston, J. and Jackson, J. D. and Johnson, K. F. and Junk, T. and Karlen, D. and Kirkby, D. and Klein, S. R. and Klempt, E. and Kowalewski, R. V. and Krauss, F. and Kreps, M. and Krusche, B. and Kuyanov, Yu. V. and Kwon, Y. and Lahav, O. and Laiho, J. and Langacker, P. and Liddle, A. and Ligeti, Z. and Liss, T. M. and Littenberg, L. and Lugovsky, K. S. and Lugovsky, S. B. and Mannel, T. and Manohar, A. V. and Marciano, W. J. and Martin, A. D. and Masoni, A. and Matthews, J. and Milstead, D. and Miquel, R. and M\"onig, K. and Moortgat, F. and Nakamura, K. and Narain, M. and Nason, P. and Navas, S. and Neubert, M. and Nevski, P. and Nir, Y. and Olive, K. A. and Pape, L. and Parsons, J. and Patrignani, C. and Peacock, J. A. and Petcov, S. T. and Piepke, A. and Pomarol, A. and Punzi, G. and Quadt, A. and Raby, S. and Raffelt, G. and Ratcliff, B. N. and Richardson, P. and Roesler, S. and Rolli, S. and Romaniouk, A. and Rosenberg, L. J. and Rosner, J. L. and Sachrajda, C. T. and Sakai, Y. and Salam, G. P. and Sarkar, S. and Sauli, F. and Schneider, O. and Scholberg, K. and Scott, D. and Seligman, W. G. and Shaevitz, M. H. and Sharpe, S. R. and Silari, M. and Sj\"ostrand, T. and Skands, P. and Smith, J. G. and Smoot, G. F. and Spanier, S. and Spieler, H. and Stahl, A. and Stanev, T. and Stone, S. L. and Sumiyoshi, T. and Syphers, M. J. and Takahashi, F. and Tanabashi, M. and Terning, J. and Titov, M. and Tkachenko, N. P. and T\"ornqvist, N. A. and Tovey, D. and Valencia, G. and van Bibber, K. and Venanzoni, G. and Vincter, M. G. and Vogel, P. and Vogt, A. and Walkowiak, W. and Walter, C. W. and Ward, D. R. and Watari, T. and Weiglein, G. and Weinberg, E. J. and Wiencke, L. R. and Wolfenstein, L. and Womersley, J. and Woody, C. L. and Workman, R. L. and Yamamoto, A. and Zeller, G. P. and Zenin, O. V. and Zhang, J. and Zhu, R. -Y. and Harper, G. and Lugovsky, V. S. and Schaffner, P.},     url = {http://link.aps.org/doi/10.1103/PhysRevD.86.010001},


\bibitem{pdg11strFn} K. Nakamura et al. (PDG), \href{http://pdg.lbl.gov/2011/reviews/rpp2011-rev-structure-functions.pdf}{JP G37, 075021 (2010) and 2011 partial update for the 2012 edition}    

%http://cds.cern.ch/record/1299148/export/hx?ln=en        author        = "Nakamura, K and Hagiwara, K and Hikasa, K and Murayama, H and Tanabashi, M and Watari, T and Amsler, C and Antonelli, M and Asner, D M and Baer, H and Band, H R and Barnett, R M and Basaglia, T and Bergren, E and Beringer, J and Bernardi, G and Bertl, W and Bichsel, H and Biebel, O and Blucher, E and Blusk, S and Cahn, R N and Carena, M and Ceccucci, A and Chakraborty, D and Chen, M-C and Chivukula, R S and Cowan, G and Dahl, O and D’Ambrosio, G and Damour, T and de Florian, D and de Gouvêa, A and DeGrand, T and Dissertori, G and Dobrescu, B and Doser, M and Drees, M and Edwards, D A and Eidelman, S and Erler, J and Ezhela, V V and Fetscher, W and Fields, B D and Foster, B and Gaisser, T K and Garren, L and Gerber, H-J and Gerbier, G and Gherghetta, T and Giudice, G F and Golwala, S and Goodman, M and Grab, C and Gritsan, A V and Grivaz, J-F and Groom, D E and Grünewald, M and Gurtu, A and Gutsche, T and Haber, H E and Hagmann, C and Hayes, K G and Heffner, M and Heltsley, B and Hernández-Rey, J J and Höcker, A and Holder, J and Huston, J and Jackson, J D and Johnson, K F and Junk, T and Karle, A and Karlen, D and Kayser, B and Kirkby, D and Klein, S R and Kolda, C and Kowalewski, R V and Krusche, B and Kuyanov, Yu V and Kwon, Y and Lahav, O and Langacker, P and Liddle, A and Ligeti, Z and Lin, C-J and Liss, T M and Littenberg, L and Lugovsky, K S and Lugovsky, S B and Lys, J and Mahlke, H and Mannel, T and Manohar, A V and Marciano, W J and Martin, A D and Masoni, A and Milstead, D and Miquel, R and Mönig, K and Narain, M and Nason, P and Navas, S and Nevski, P and Nir, Y and Olive, K A and Pape, L and Patrignani, C and Peacock, J A and Petcov, S T and Piepke, A and Punzi, G and Quadt, A and Raby, S and Raffelt, G and Ratcliff, B N and Richardson, P and Roesler, S and Rolli, S and Romaniouk, A and Rosenberg, L J and Rosner, J L and Sachrajda, C T and Sakai, Y and Salam, G P and Sarkar, S and Sauli, F and Schneider, O and Scholberg, K and Scott, D and Seligman, W G and Shaevitz, M H and Silari, M and Sjöstrand, T and Smith, J G and Smoot, G F and Spanier, S and Spieler, H and Stahl, A and Stanev, T and Stone, S L and Sumiyoshi, T and Syphers, M J and Terning, J and Titov, M and Tkachenko, N P and Törnqvist, N A and Tovey, D and Trippe, T G and Valencia, G and van Bibber, K and Venanzoni, G and Vincter, M G and Vogel, P and Vogt, A and Walkowiak, W and Walter, C W and Ward, D R and Webber, B R and Weiglein, G and Weinberg, E J and Wells, J D and Wheeler, A and Wiencke, L R and Wohl, C G and Wolfenstein, L and Womersley, J and Woody, C L and Workman, R L and Yamamoto, A and Yao, W-M and Zenin, O V and Zhang, J and Zhu, R-Y and Zyla, P A and Harper, G and Lugovsky, V S and Schaffner, P",
\bibitem{Nakamura:1299148}
      Nakamura, K and others",Review of Particle Physics, 2010-2011. Review of Particle Properties,
      J. Phys. G, Particle Data Group. Berkeley, 7A (37) (2010)

\bibitem{pdg12Res} J. Beringer et al. (PDG), \href{http://pdg.lbl.gov/2012/reviews/rpp2012-rev-n-delta-resonances.pdf}{PR \textbf{D86}, 010001 (2012)}


%From Proceedings 
\bibitem{procKazimi}\href{http://accelconf.web.cern.ch/AccelConf/e04/PAPERS/TUPLT164.PDF}  {R. Kazimi \etal}. CEBAF Injector Achieved World's Best Beam Quality for Three Simultaneous Beams with a Wide Range of Bunch Charges, Proceedings of EPAC 2004, Lucerne, Switzerland
%An article in a conference proceedings.
%Required fields: author, title, booktitle, year
%Optional fields: editor, volume/number, series, pages, address, month, organization, publisher, note, key

\bibitem{HosodaYamamoto66} M. Hosoda and K. Yamamoto, Prog. Theor. Phys. (Kyoto) \textbf{30}, 425 (1966)

\bibitem{KuhnHUGS} S. E. Kuhn, Nucleon Structure Functions: Experiments and Models, Proceedings of the 12th Annual HUGS at CEBAF, 1997
%Unpublished{ Kuhn:HUGS,

\bibitem{bkAnselmino} M. Anselmino \etal Three-Dimensional Partonic Structure of the Nucleon, Proceedings of the International School of Physics "Enrico Fermi", 2011, Varenna On Lake Como Italy.%IOS Press, 2012 %http://books.google.com/books?id=h1Te-D5Nf-EC&printsec=frontcover#v=onepage&q&f=false

% Technotes
\bibitem{KuhnEG4ana} S. E. Kuhn, K. Adhikari,Data Analysis for EG4 - extraction of g1 from data  	url = "{https://clasweb.jlab.org/rungroups/eg4/wiki/index.php/Technotes\_and\_Reports}", \href{https://userweb.jlab.org/\~kuhn/EG4/EG4\_analysis.pdf}{https://clasweb.jlab.org/rungroups/eg4/wiki/index.php/Technotes\_and\_Reports}


%Proposals:
\bibitem{propE06_017} A. Deur, et al. 2005 Jefferson Lab proposal PR06-017  % The deuteron-target EG4 proposal  %http://www.jlab.org/exp_prog/proposals/06prop.html  Misc idea from Mike's *.bib file    	url = "http://www.jlab.org/exp_prog/proposals/06/PR06-017.pdf",

\bibitem{propE03_006} M. Anghinolfi , et al. 2003 Jefferson Lab proposal E03-006 %The proton-target EG4 proposal  %http://www.jlab.org/exp_prog/proposals/03prop.html     	url = "http://www.jlab.org/exp_prog/proposals/03/PR03-006.pdf",

\bibitem{propE97_110} J.P. Chen, et al. 1997 Jefferson Lab proposal PR97-110 %Available at http://hallaweb.jlab.org/physics/experiments/he3/gdh/PR97-110.pdf %http://www.jlab.org/exp_prog/proposals/97/PR97-110.pdf % http://www.jlab.org/exp_prog/proposals/97prop.html http://www.jlab.org/exp_prog/proposals/       	url = "http://www.jlab.org/exp_prog/proposals/97/PR97-110.pdf",

%Websites
%misc
%    For use when nothing else fits.
%    Required fields: none
%    Optional fields: author, title, howpublished, month, year, note, key
\bibitem{eg4Hm_wb} \href{http://clasweb.jlab.org/shift/eg4/}{http://clasweb.jlab.org/shift/eg4/}   url = "http://clasweb.jlab.org/shift/eg4/",

\bibitem{eg4wiki} \href{https://clasweb.jlab.org/rungroups/eg4/wiki/index.php/Main\_Page}{https://clasweb.jlab.org/rungroups/eg4/wiki/index.php/Main\_Page}   url = "{https://clasweb.jlab.org/rungroups/eg4/wiki/index.php/Main\_Page}",

\bibitem{cebaf2_wb} \href{http://www.aip.org/png/html/cebaf.htm}{http://www.aip.org/png/html/cebaf.htm}     url = "http://www.aip.org/png/html/cebaf.htm",

%\bibitem{kuhnDvcs_wb} http://clasweb.jlab.org/rungroups/eg1-dvcs/wiki/index.php/\\Raster$\_$Correction:$\_$last$\_$update$\_$June$\_$16$\_$2009
\bibitem{gsimMH_wb} M. Holtrop, GSIM: CLAS GEANT Simulation, \href{http://nuclear.unh.edu/\textasciitilde maurik/gsim\_info.shtml}{http://nuclear.unh.edu/\~maurik/gsim\_info.shtml} 
%\bibitem{gsimMH_wb} M. Holtrop, GSIM: CLAS GEANT Simulation, \url{http://nuclear.unh.edu/\~maurik/gsim\_info.shtml}     url = "{http://nuclear.unh.edu/\~maurik/gsim\_info.shtml}",

%http://tex.stackexchange.com/questions/9363/how-does-one-insert-a-backslash-or-a-tilde-into-latex
% Solved the tilda problem using 'url' (got idea from above link & http://en.wikibooks.org/wiki/LaTeX/Hyperlinks#.5Curl)
\bibitem{jlabVocab_wb} \href{http://www.jlab.org/news/facts/vocab.html}{http://www.jlab.org/news/facts/vocab.html}    url = "http://www.jlab.org/news/facts/vocab.html",

%\bibitem{DC1_wb} \href{http://www-meg.phys.cmu.edu/\textasciitilde bellis/dc/dcintro.html}{http://www-meg.phys.cmu.edu/\~bellis/dc/dcintro.html}  %Tilda didn't work right with href, so I am using the following 
\bibitem{DC1_wb} \url{http://www-meg.phys.cmu.edu/\~bellis/dc/dcintro.html}     url = "http://www-meg.phys.cmu.edu/\~bellis/dc/dcintro.html",

\bibitem{DC2_wb} \href{http://ikpe1101.ikp.kfa-juelich.de/cosy-11/exp/drift\_chambers/DriftChambers\_E.html}                {http://ikpe1101.ikp.kfa-juelich.de/cosy-11/exp/drift\_chambers/DriftChambers\_E.html}    url = "http://ikpe1101.ikp.kfa-juelich.de/cosy-11/exp/drift\_chambers/DriftChambers\_E.html",
                
\bibitem{uvaTgtHA_wb} \href{https://hallaweb.jlab.org/wiki/index.php/Practical\_Primer\_on\_the\_UVa\_Target}                 {https://hallaweb.jlab.org/wiki/index.php/Practical\_Primer\_on\_the\_UVa\_Target}
                
\bibitem{schlpClas_wb} \href{http://www.scholarpedia.org/article/The\_Thomas\_Jefferson\_National\_Accelerator\_Facility}                     {http://www.scholarpedia.org/article/The\_Thomas\_Jefferson\_National\_Accelerator\_Facility} %http://www.scholarpedia.org/w/index.php?title=The_Thomas_Jefferson_National_Accelerator_Facility&action=cite&rev=91872

                    
\bibitem{bpmMSpata_wb} M. F. Spata, TJNAF, \href{http://cdsweb.cern.ch/record/586314/files/p101.pdf}{http://cdsweb.cern.ch/record/586314/files/p101.pdf} %https://cds.cern.ch/record/586314/export/hx?ln=en

\bibitem{bpmRUrsicEtc_wb} R. Ursic \etal. \href{http://epaper.kek.jp/pac97/papers/pdf/9P089.PDF}{1 nA Beam Position Monitory System}, TJNAF



% Computation related
\bibitem{bos} V. Blobel \etal. The BOS system for the CLAS detector: Dynamic Memory Management, (1995).

%Private Communications
\bibitem{kuhn_dodge_pc} S. E. Kuhn and G. E. Dodge, Private communications. %Multiply defined error (also defined in bibli.tex in chap6expSetup

\bibitem{pComKuhn} S. E. Kuhn, Private communications.

\bibitem{pComKuhn} S. E. Kuhn, Private communications.

\bibitem{pComDodge} G. E. Dodge, Private communications.

\bibitem{deurSlifRip_pc} A. Deur, K. Slifer and M. Ripani (EG4 spokespersons), Private communications.

\bibitem{HK_dXs_extr} \href{http://wwwold.jlab.org/Hall-B/secure/eg4/hkkang/dXs\_extraction\_2nd.pdf}{H. Kang}, Procedure for extraction of difference of cross sections.



%   From: https://userweb.jlab.org/~kuhn/EG4/EG4_analysis.pdf by SEK & KPA
\bibitem{EG4:ref} M. Anghinolfi \etal ``The GDH Sum Rule with Nearly-Real Photons and the Proton $g_1$ Structure Function at Low Momentum Transfer,'' CLAS Proposal PR-03-006 (2003). %It seems repeated       	url = "http://www.jlab.org/exp_prog/proposals/03/PR03-006.pdf",

\bibitem{panal} R. Fersch, ``Measurement of Inclusive Proton Double-Spin Asymmetries and Polarized Structure Functions in the CLAS EG1b Experiment'', 2012. URL: {\texttt http://www.jlab.org/Hall-B/secure/eg1/EG2000/fersch/softwarenote/AnalysisNote/}

\bibitem{PolNit:ref} K. Abe \etal, Measurements of the proton and deuteron spin structure functions ${g}_{1}$ and ${g}_{2}$, Phys. Rev. D \textbf{58}, 112003 (1998).     

\bibitem{Mayer} M. Mayer, CLAS NOTE 2012 - 004 (2012).  %https://misportal.jlab.org/ul/Physics/Hall-B/clas/index.cfm?note_year=2012


\bibitem{Kuchto:ref} T.V. Kuchto and N.M. Shumeiko,  ``Radiative Effects in Deep Inelastic Scattering of Polarized Leptons by Polarized Nucleons,'' \npb{219}, 412 (1983).       	url = "http://www.sciencedirect.com/science/article/pii/0550321383906508",

\bibitem{MoTsai:ref} L.W. Mo and Y.S. Tsai, ``Radiative Corrections to Elastic and Inelastic $ep$ and $\mu p$ Scattering,'' Rev. Mod. Phys. \textbf{41}, 205 (1969).        url = {http://link.aps.org/doi/10.1103/RevModPhys.41.205},


%http://inspirehep.net/search?p=find+eprint+0711.0159
\bibitem{Bosted:2007xd}
        Bosted, P.E. and Christy, M.E., Empirical fit to inelastic electron-deuteron and  electron-neutron resonance region transverse cross-sections,
        10.1103/PhysRevC.77.065206, (2008)



%============ Following brought from TechNotes/deutContam.tex 
%\bibitem{PDG} Particle Data Group, LBL.
\bibitem{sarahTgt} \href{http://clasweb.jlab.org/rungroups/eg4/wiki/index.php/October\_14\%2C\_2011\#Target\_Composition}{http://clasweb.jlab.org/rungroups/eg4/wiki/index.php/October\_14\%2C\_2011}

\bibitem{bostedD2Cont} \href{http://wwwold.jlab.org/Hall-B/secure/eg1-dvcs/technotes/hind/hind.pdf}{P. Bosted, \nh3 correction for \nd3 target}, EG1-DVCS Technical Note \# 017

\bibitem{koiralaD2Cont} \href{http://wwwold.jlab.org/Hall-B/secure/eg1-dvcs/skoirala/ND3Contam/WideContamDist.gif}{S. Koirala's work on Deuteron contamination (EG1-DVCS)}.  	url = "\url{http://www.jlab.org/Hall-B/secure/eg1-dvcs/skoirala/FilesForWiki/Contamination.pdf}"


%\bibitem{pComKuhn} S. E. Kuhn, Private communications.



%CLAS Notes
\bibitem{multscat_cn} P. ~Bosted {\em et al.}, CLAS-Note 2006-006 JLAB (2006). %kp: \em : Emphasis (toggles between \it and \rm).

\bibitem{e6momcor_cn} A. ~Klimenko {\em et al.}, CLAS-Note 2003-005 JLAB (2003).

\bibitem{rstcor_cn} P. ~Bosted {\em et al.}, CLAS-Note 2003-008 JLAB (2003).

%**********************
%kp: From http://web.mit.edu/olh/Latex/ess-latex.html
%     To emphasize some text in your document, use the \em (``emphasis'') command. It normally italicizes that 
%     text, but using \em is preferred to using \it (see below), because you can nest \em commands:
%           {\em This sentence is {\em emphasized}, with emphasis on the word {\em emphasized}.}
%  ********************


%Theses
\bibitem{skabelin_th} A. ~Skabelin, GDH Integral on the Proton from Cross Section Differences. PhD thesis, Massachusetts Institute of Techology, (2000) %Megh: Tilda (~) gives a half-space

\bibitem{klimenko_th} A. ~Klimenko, Electron Scattering From a High-Momentum Neutron in Deuterium. PhD thesis, Old Dominion University, (2004)

%\bibitem{vipuli_th} K. G. V. ~Dharmawardane, Spin Structure Functions of the Deuteron Measured with CLAS in and Above the Resonance Region. PhD thesis, Old Dominion University, (2004)
%\bibitem{fersch_th} R. ~G. ~Fersch, Jr., Measurement of Inclusive Proton Double-Spin Asymmetries and Polarized Structure Functions. PhD thesis, The College of William and Mary, (2008)
%\bibitem{nevzat_th} N. ~Guler, Spin Structure of the Deuteron. PhD thesis, Old Dominion University, (2009)
%\bibitem{guler_th} N. ~Guler, Spin Structure of the Deuteron. PhD thesis, Old Dominion University, (2009)
%\bibitem{tkachenko_th} S. ~Tkachenko, Neutron Structure Functions Measured with Spectator Tagging. PhD 
%thesis, Old Dominion University, (2009)
\bibitem{slava_th} S. ~Tkachenko, Neutron Structure Functions Measured with Spectator Tagging. PhD thesis, Old Dominion University, (2009)

%Books
%\bibitem{bogdan_bk} Bogdan Povh, Klaus Rith, Christoph Scholz, Frank Zetsche: Particles and Nuclei (Springer, New York 1995)
%\bibitem{halzen} F. Halzen and A. D. Martin, Quarks and Leptons, New York: John Wiley & Sons (1979). %From Nevzat's thesis (pdf)
%\bibitem{halzen_bk} F. Halzen and A. D. Martin: Quarks and Leptons (John Wiley $\&$ Sons, New York 1979).
%To get any special character such as &, *, $ or # etc, put a slash '\' in front of it

%Websites
\bibitem{kuhnDvcs_wb} http://clasweb.jlab.org/rungroups/eg1-dvcs/wiki/index.php/\\Raster$\_$Correction:$\_$last$\_$update$\_$June$\_$16$\_$2009

%The following are all Megh's Bibliographic list

%kp \bibitem{will} W.~K.~Brooks {\em et al.}, Beyond the Born approximation : A precision
%kp comparison of $e+ p$ and $e- p$ scattering in CLAS, proposal for an experiment E-04-116 at Jlab.
%kp \bibitem{guichon} P.~A.~M.~Guuiuchon, M.~Vanderhaeghen, Phys. Rev. Lett.\textbf{91} 142303 (2003).
%kp \bibitem{rosenbluth} M.~N.~Rosenbluth, Phys. Rev.\textbf{79}, 615 (1950).
%kp \bibitem{gayou} O. ~Gayou, Measurement of the proton form factors ratio upto
%kp $Q^2=5.6 GeV^2$ by recoil polarimetry. PhD thesis, The College of William and Mary, (2002)
%kp \bibitem{christy} Christy {\em et al.}, Phys. Rev. \textbf{C 70}, 015206 (2004).
%kp \bibitem{qatan} I. ~A. ~Qattan {\em et al.} Phys. Rev. Lett. \textbf{94}, 142301 (2005).
%kp \bibitem{jones} M.~K.~Jones {\em et al.} Phys. Rev. Lett, \textbf{84}, 7 (2000).
%kp \bibitem{andivahis} L. ~Andivahis {\em et al.} Phys. Rev. \textbf{D50}, 9 (1994).
%kp \bibitem{bogdan} Bogdan Povh, Klaus Rith, Christoph Scholz, Frank Zetsche: Particles and Nuclei(Springer, New York 1995)
%kp \bibitem{jarr} J.~Arrington, Phys. Rev. C68, 034325 (2003)
%kp \bibitem{qatan_th} I. ~A. ~Qattan, Precision Rosenbluth measurement of
%kp proton elastic electromagnetic form factors and their ratio. PhD thesis, Northwesterm University, (2005)
%kp \bibitem{mo} L.~W.~Mo, Y.~S.~Tsai, Rev. Mod. Phys. \textbf{41}, 205 (1969).
%kp \bibitem{tsai} Y.~S.~Tsai, Phys. Rev. \textbf{122}, 1898 (1961).
%kp \bibitem{jarri} J.~Arrington, Phys. Rev. C69, 032201 (2004)



%\bibitem{jarri} J.~Arrington, Phys. Rev. C68, 034325 (2003)
%[1] W. K Brooks et al. Beyond the Born approximation : A precision
%comparison of $e+ p$ and $e- p$ scattering in CLAS, proposal for an
%experiment E-04-116 at Jlab.\newline
%[2] P. A. M Guichon and M. Vanderhaeghen, Phys. Rev. Lett. 91,
%142303(2003)\newline 

%[3] P. G. Blunden, W. Melnitchouk, and J. A. Tjon,
%arXiv:nucl-th/0506039\newline
%[4] J. Arrington, Phys. Rev. C68, 034325(2003)\newline
%[5] M.N. Rosenbluth, Phys. Rev. 79, 615(1950)\newline
%[6] O. Gayou, Measurement of the proton form factors ratio upto
%$Q^2=5.6 GeV^2$ by recoil polarimetry. PhD thesis, The College of
%William and Mary,2002\newline
%[7] Christy et al. Phys. Rev. C70,015206(2004)\newline
%[8] I. A Qattan et. al. Phys. Rev. Lett. PRL94, 142301(2005)\newline
%[9] M.K Jones et al. Phys. Rev. Lett, 84,7(2000)\newline
%[10] L. Andivahis et al. Phys. Rev. D50,9(1994)\newline
%[11] Bogdan Povh, Klaus Rith, Christoph Scholz, Frank Zetsche:
%Particles and Nuclei(Springer, New York 1995)\newline
%[12] J. Arrington, Phys. Rev. C69, 032201(2004)\newline
%[13] Chen et al., arXiv:hep-ph/0403058(2004)

%==========================================================
%  Added while doing the corrections 11/21/13   %  url = {http://link.aps.org/doi/10.1103/PhysRevLett.18.1174},
% Theory of the Gottfied sum rule   author = {\href{http://link.aps.org/doi/10.1103/PhysRevLett.18.1174}{Gottfried, Kurt}},
\bibitem{PhysRevLett.18.1174}
  Gottfried, Kurt, Sum Rule for High-Energy Electron-Proton Scattering,
  10.1103/PhysRevLett.18.1174, 1967    

% Experimental test and violation of the Gottfried sum rule http://prd.aps.org/abstract/PRD/v50/i1/pR1_1
%  author = {Arneodo, M. and Arvidson, A. and Badelek, B. and Ballintijn__kpAtf__, M. and Baum__kpAtf__, G. and Beaufays, J. and Bird, I. G. and Bj\"orkholm, P. and Botje, M. and Broggini, C. and Br\"uckner__kpAtf__, W. and Br\"ull, A. and Burger, W. J. and Ciborowski, J. and van Dantzig__kpAtf__, R. and Dyring, A. and Engelien, H. and Ferrero, M. I. and Fluri__kpAtf__, L. and Gaul__kpAtf__, U. and Granier, T. and von Harrach, D. and van der Heijden, M. and Heusch, C. and Ingram, Q. and Janson-Prytz, K. and de Jong__kpAtf__, M. and Kabuss, E. M. and Kaiser__kpAtf__, R. and Ketel__kpAtf__, T. J. and Klein__kpAtf__, F. and Kullander, S. and Landgraf__kpAtf__, U. and Lindqvist, T. and Mallot, G. K. and Mariotti, C. and van Middelkoop, G. and Milsztajn, A. and Mizuno, Y. and Nassalski, J. and Oberski__kpAtf__, J. and Nowotny, D. and Paic__kpAtf__, A. and Peroni, C. and Povh, B. and Rieger, R. and Rith, K. and R\"ohrich, K. and Rondio, E. and Ropelewski, L. and Sandacz, A. and Sanders, D. and Scholz__kpAtf__, C. and Schumacher, R. and Seitz__kpAtf__, R. and Sever, F. and Shibata__kpAtf__, T.-A. and Siebler__kpAtf__, M. and Simon__kpAtf__, A. and Staiano, A. and Szleper, M. and Tzamouranis, Y. and Virchaux, M. and Vuilleumier__kpAtf__, J. L. and Walcher__kpAtf__, T. and Windmolders__kpAtf__, R. and Witzmann__kpAtf__, A. and Zetsche__kpAtf__, F.},            url = {http://link.aps.org/doi/10.1103/PhysRevD.50.R1},
\bibitem{PhysRevD.50.R1}
     M. Arneodo \etal, Reevaluation of the Gottfried sum,
      Phys. Rev. D, American Physical Society, (1994)

% http://inspirehep.net/record/571583/export/hx  (For Wien Filter citation) 11/22/13
\bibitem{Leemann:2001dg},
      Leemann, C.W. and Douglas, D.R. and Krafft, G.A., The Continuous Electron Beam Accelerator Facility: CEBAF at the Jefferson Laboratory,
      Ann.Rev.Nucl.Part.Sci. (2001)

%============= 11/27/13
% http://inspirehep.net/search?p=find+irn+533831
\bibitem{Dokshitzer:1977sg}
      Dokshitzer, Yuri L., Calculation of the Structure Functions for Deep
                        Inelastic Scattering and e+ e- Annihilation by
                        Perturbation Theory in Quantum Chromodynamics.,
      Sov.Phys.JETP, (1977)

% http://inspirehep.net/search?p=find+irn+78573
\bibitem{Gribov:1972ri}
      Gribov, V.N. and Lipatov, L.N.,
      Deep inelastic e p scattering in perturbation theory,
      Sov.J.Nucl.Phys., (1972)

% http://inspirehep.net/search?p=find+irn+224570
\bibitem{Altarelli:1977zs}
      Altarelli, Guido and Parisi, G.,
      Asymptotic Freedom in Parton Language,
      Nucl.Phys., (1977) 

% 12/1/13: Latest cross-section model used (for analysis, for RCSLACPOL etc) reference
\bibitem{EG1bProt}  %replace this with the published or to-be-published paper references
	R. G. Fersch \etal, Precise Determination of Proton Spin Structure Functions at Low to Moderate $Q^2$ with CLAS, (2012)

\bibitem{EG1bDeut}
	N. Guler \etal, Precise Determination of Deuteron and Neutron Spin Structure Functions at Low to Moderate $Q^2$ with CLAS, (2013)


%From Mike's .bib file
\bibitem{leo1994techniques}
        Leo, William R, Techniques for nuclear and particle physics experiments: a how-to approach, Springer, (1994)


%  author = {Dutz, H. and Helbing, K. and Krimmer, J. and Speckner, T. and Zeitler, G. and Ahrens, J. and Altieri, S. and Annand, J. R. M. and Anton, G. and Arends, H.-J. and Beck, R. and Bock, A. and Bradtke, C. and Braghieri, A. and v. Drachenfels, W. and Frommberger, F. and Godo, M. and Goertz, S. and Grabmayr, P. and Hasegawa, S. and Hansen, K. and Harmsen, J. and Heid, E. and Hillert, W. and Holvoet, H. and Horikawa, N. and Iwata, T. and Hoorebeke, L. Van and d'Hose, N. and Jennewein, P. and Kiel, B. and Klein, F. and Kondratiev, R. and Lang, M. and Lannoy, B. and Leukel, R. and Lisin, V. and Menze, D. and Meyer, W. and Michel, T. and Naumann, J. and Panzeri, A. and Pedroni, P. and Pinelli, T. and Preobrajenski, I. and Radtke, E. and Reicherz, G. and Rohlof, C. and Rostomyan, T. and Sauer, M. and Schoch, B. and Schumacher, M. and Tamas, G. and Thomas, A. and van de Vyver, R. and Weihofen, W. and Zapadtka, F.},  http://prl.aps.org/abstract/PRL/v91/i19/e192001
\bibitem{PhysRevLett.91.192001}
        Dutz, H. \etal, First Measurement of the Gerasimov-Drell-Hearn Sum Rule for $^{1}\mathrm{H}$ from 0.7 to 1.8~GeV at ELSA,
        Phys. Rev. Lett., American Physical Society, (2003)

%http://prl.aps.org/abstract/PRL/v94/i16/e162001   author = {Dutz, H. and Helbing, K. and Krimmer, J. and Speckner, T. and Zeitler, G. and Ahrens, J. and Altieri, S. and Annand, J. R. M. and Anton, G. and Arends, H.-J. and Beck, R. and Bock, A. and Bradtke, C. and Braghieri, A. and v. Drachenfels, W. and Frommberger, F. and Godo, M. and Goertz, S. and Grabmayr, P. and Hasegawa, S. and Hansen, K. and Harmsen, J. and Heid, E. and Hillert, W. and Holvoet, H. and Horikawa, N. and Iwata, T. and Van Hoorebeke, L. and d'Hose, N. and Jennewein, P. and Kiel, B. and Klein, F. and Kondratiev, R. and Lang, M. and Lannoy, B. and Leukel, R. and Lisin, V. and Menze, D. and Meyer, W. and Michel, T. and Naumann, J. and Panzeri, A. and Pedroni, P. and Pinelli, T. and Preobrajenski, I. and Radtke, E. and Reicherz, G. and Rohlof, C. and Rostomyan, T. and Sauer, M. and Schoch, B. and Schumacher, M. and Tamas, G. and Thomas, A. and van de Vyver, R. and Weihofen, W. and Zapadtka, F.}, 
\bibitem{PhysRevLett.94.162001}
        Dutz, H. \etal, Measurement of Helicity-Dependent Photoabsorption Cross Sections on the Neutron from 815 to 1825~MeV, 
        Phys. Rev. Lett., American Physical Society, (2005)
 
%http://inspirehep.net/search?p=find+eprint+NUCL-TH/0406059
\bibitem{Drechsel:2004ki},
      Drechsel, Dieter and Tiator, Lothar,
      The Gerasimov-Drell-Hearn sum rule and the spin structure of the nucleon,
      Ann.Rev.Nucl.Part.Sci., (2004)

% http://scitation.aip.org/content/aip/proceeding/aipcp/10.1063/1.3203304 ->  http://prl.aps.org/abstract/PRL/v102/i17/e172002   ->   author = {Hoblit, S. and Sandorfi, A. M. and Ardashev, K. and Bade, C. and Bartalini, O. and Blecher, M. and Caracappa, A. and D'Angelo, A. and d'Angelo, A. and Di Salvo, R. and Fantini, A. and Gibson, C. and Gl\"uckler, H. and Hicks, K. and Honig, A. and Kageya, T. and Khandaker, M. and Kistner, O. C. and Kizilgul, S. and Kucuker, S. and Lehmann, A. and Lowry, M. and Lucas, M. and Mahon, J. and Miceli, L. and Moricciani, D. and Norum, B. and Pap, M. and Preedom, B. and Seyfarth, H. and Schaerf, C. and Str\"oher, H. and Thorn, C. E. and Whisnant, C. S. and Wang, K. and Wei, X.},

\bibitem{PhysRevLett.102.172002}
        Hoblit, S. \etal, %Measurements of \stackrel{$\rightarrow${}}{\mathbf{H}}\stackrel{$\rightarrow${}}{\mathbf{D}}(\stackrel{$\rightarrow${}}{$\gamma${}},$\pi${}) and Implications for the Convergence of the Gerasimov-Drell-Hern Integral,
        %Measurements of H⃗ D⃗ (γ⃗ ,π) and Implications for the Convergence of the Gerasimov-Drell-Hern Integral,
        Measurements of HD($\gamma,\pi$) and Implications for the Convergence of the Gerasimov-Drell-Hern Integral,
        LEGS-Spin Collaboration, Phys. Rev. Lett., American Physical Society (2009)


% 1/22/14  (OPE, Higher Twists: deplgze)
%http://inspirehep.net/record/441311/export/hx
\bibitem{Ji:1997gs}
      Ji, Xiang-Dong and Melnitchouk, W., Spin dependent twist four matrix elements from g1 data  in the resonance region,
      Phys.Rev., (1997)

%http://inspirehep.net/record/647784/export/hx
\bibitem{Meziani:2004ne},
      Meziani, Z.E. \etal, Higher twists and color polarizabilities in the  neutron,
      Phys.Lett.,JLAB-PHY-04-10, (2005)
%http://inspirehep.net/search?p=find+eprint+HEP-PH/9702435
\bibitem{Larin:1997qq}
      Larin, S.A. and van Ritbergen, T. and Vermaseren, J.A.M.,
     The Alpha-s**3 approximation of quantum chromodynamics
                        to the Ellis-Jaffe sum rule,
      Phys.Lett., (1997)

% http://inspirehep.net/search?p=find+eprint+HEP-PH/9403383
\bibitem{Larin:1994dr},
      Larin, S.A., The Next-to-leading QCD approximation to the Ellis-Jaffe sum rule,
      Phys.Lett., (1994)
