%\chapter{Kinematic Corrections}
\section{Kinematic Corrections}
\label{cha:KineCor}
The reconstructed event vertices and associated particle 4-momenta are slightly off from their true values for several reasons. First, % of all, %SEK
RECSIS does not take into account the fact that the beam is rastered in polarized target experiments. Next, any 
imperfections and mis-alignments of detectors and other components of the experimental set-up are not accounted for. 
Furthermore, the torus field map is not known precisely. 
In addition, the effects of multiple-scattering and particle energy losses are not considered in RECSIS. %Finally, RECSIS itself has imperfections inherent in its algorithm. %SEK: Unless you want to explain, leave out.
Therefore, to get more accurate results from the data analysis, the data quality must be improved by applying various kinematic corrections. Following is the list of the corrections that were applied for %is applied for each particle from our data 
the analysis:

\begin{enumerate}
\item Incoming (beam) energy loss correction (due to ionization) 
\item Tracking corrections
%%%%\begin{enumerate}
%%%%\item Beam off-set correction % equivalent to Raster correction?
%\item Drift chamber dependent momentum correction
%\item Z-vertex correction
%%%%\item Solenoid axis tilt correction
%%%%\item Solenoid axis offset correction
%%%%\end{enumerate}
%\item Stray magnetic field correction 
\item Drift chamber dependent momentum correction
%\item Multiple scattering correction (Not considered because, we are looking at electron-only inclusive events)
\item Outgoing energy loss correction (due to ionization after scattering) %/reaction))
\end{enumerate}



%\section{Incoming Energy Loss Correction}
\subsection{Incoming Energy Loss Correction}
%Out of these corrections, the first one
The first correction listed above considers the loss of beam energy due to atomic collisions before the actual nuclear scattering takes place. %As an adjustment for the loss, an estimate of 2 MeV
A good estimate for this loss is 2 MeV on average \cite{pComKuhn, pComBosted}, which is subtracted from the nominal beam energy. This correction is applied during the analysis whenever the beam energy is involved\footnote{The beam energies that we used were derived from the Hall A and Hall C Tiefenback energies  or the MDSY1c or MDSY3c energies\cite{eg4Ebeam}}, %For more info, read X. Zheng's analysis note around page 35.
and therefore it is not included in the correction package described below.





%\input{rasterCorrection.tex}
%\input{trackingCorrectionsEG4.tex}
\input{trackingCorrectionsEG4_shorter.tex}
%\input{kinematicCorrectionsPCor.tex}
\input{kineCor_inclusivePCor.tex}


